---
title: "Nesting success modelling"
author: "Sinchan Ghosh, Arnab Banerjee, Soumalya Mukhopadhyay, Sabyasachi Bhattacharya"
date: "28/01/2022"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Package loading
```{r}
library(keras)
library(mlbench)
library(dplyr)
library(magrittr)
library(neuralnet)
library(NeuralNetTools)
library(plotly)
library(matrixStats)
library(boot)
library(plyr)
library(GGally)
library(ggbiplot)
```

#All data reading
```{r}
setwd("G:/Sinchan Ghosh/Nesting success and cooperation")
getwd()
n_dataab <- read.csv("nestingsocio.csv",header = T)
names(n_dataab)
rownames(n_dataab)=c("A","B","C","D","E","F","G","H")
```
## Data subsets
```{r}
newdfab1=subset(n_dataab,select = -c(P.F.,P.H.,P.M.,P.N.))
newdfab2=subset(n_dataab,select = -c(P.F.,P.H.,P.M.,P.F.S.M.H..S_F))
newdfab3=subset(n_dataab,select = -c(P.F.,P.H.,P.N.,P.F.S.M.H..S_F))
newdfab4=subset(n_dataab,select = -c(P.F.,P.M.,P.N.,P.F.S.M.H..S_F))
newdfab5=subset(n_dataab,select = -c(P.H.,P.M.,P.N.,P.F.S.M.H..S_F))
newdfab1%<>% mutate_if(is.factor, as.numeric)
newdfab2%<>% mutate_if(is.factor, as.numeric)
newdfab3%<>% mutate_if(is.factor, as.numeric)
newdfab4%<>% mutate_if(is.factor, as.numeric)
newdfab5%<>% mutate_if(is.factor, as.numeric)
names(newdfab1)
```
## Correlation pairwise
###All
```{r}
ggcorr(n_dataab, method = c("everything", "pearson"),label = F,
       digits = 5,geom = "tile",label_alpha = F,
       legend.position = "top",palette = "PuOr",angle=-45, size = 2,
       hjust = 1, nbreak=8
      ,layout.exp = 4)


```
###Success with all biotic
```{r}
names(n_dataab)
ggcorr(n_dataab[,c(15:22,24:28)], method = c("everything", "pearson"),label = T,
       digits = 5,geom = "circle",label_alpha = F,
       legend.position = "top",angle=-45, size = 2,
       hjust = 1,
       nbreaks = 10,layout.exp = 3)


```


#Biotic Variable set
##For reproductive success
*Except Homoptera all are correlated*
Principal components
```{r}
bio_rep=subset(n_dataab,select = c(Lepidoptera,Ant,Wasp,Bee,Damselfly,Dragonfly))
rownames(bio_rep)=c("A","B","C","D","E","F","G","H")
colnames(bio_rep)=c("Lepidoptera","Ant","Wasp","Bee","Damselfly","Dragonfly")
PC_bio_r=prcomp(bio_rep,scale. = T)
ggbiplot(pcobj = PC_bio_r,choices =1:2,obs.scale = 1, var.scale = 1, 
         ellipse = TRUE, ellipse.prob = 1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =5,
         varname.adjust = 2,labels =rownames(bio_rep),labels.size = 2.5 )
bio_r_pc=PC_bio_r$x[,c(1,2)]
bio_r_pc

```
## For Nesting, mating, and fledging 

Principal components
```{r}
bio_nmf=subset(n_dataab,select = c(Lepidoptera,Damselfly,Dragonfly))
rownames(bio_nmf)=c("A","B","C","D","E","F","G","H")
PC_bio_nmf=prcomp(bio_nmf,scale. = T)
ggbiplot(pcobj = PC_bio_nmf,choices =1:2,obs.scale = 1, var.scale = 1, 
         ellipse = TRUE, ellipse.prob = 1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =5,
         varname.adjust = 2,labels =rownames(bio_nmf),labels.size = 2.5 )
bio_n_pc=bio_m_pc=bio_f_pc=PC_bio_nmf$x[,c(1,2)]
bio_n_pc;bio_m_pc;bio_f_pc
```
## For Hatching 

Principal components
```{r}
bio_h=subset(n_dataab,select = c(Lepidoptera,Bee,Damselfly,Dragonfly))
rownames(bio_h)=c("A","B","C","D","E","F","G","H")
PC_bio_h=prcomp(bio_h,scale. = T)
ggbiplot(pcobj = PC_bio_h,choices =1:2,obs.scale = 0.5, var.scale = 0.5, 
         ellipse = TRUE, ellipse.prob = 1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =5,
         varname.adjust = 3,labels =rownames(bio_h),labels.size = 2 )
bio_h_pc=PC_bio_h$x[,c(1,2)]
bio_h_pc

```
#Abiotic variable set
##For reproductive success

```{r}
names(n_dataab)
abio=n_dataab[,c(1:14)]
rownames(abio)=c("A","B","C","D","E","F","G","H")
colnames(abio)=c("pH","Electrical conductivity","Iron","Aluminium","Carbon","Nitrogen","Calcium","Potassium","Sodium","Magnesium","Cation exchange capacity","Sand","Silt","Clay")
abio_rep=subset(abio,select=c(Carbon,Nitrogen))
PC_abio_r=prcomp(abio_rep,scale. = T)
ggbiplot(pcobj = PC_abio_r,choices =1:2,obs.scale = 0.5, var.scale = 1, 
         ellipse = TRUE, ellipse.prob = 1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =5,
         varname.adjust = 2,labels =rownames(abio_rep),labels.size = 2.5 )
abio_r_pc=PC_abio_r$x[,c(1,2)]
abio_r_pc

```
##for Nesting
```{r}
abio_n=subset(abio,select = c(Clay, Sand, Magnesium, Carbon, Nitrogen, Iron,pH))
PC_abio_n=prcomp(abio_n,scale. = T)
ggbiplot(pcobj = PC_abio_n,choices =1:2,obs.scale = 0.5, var.scale = 1, 
         ellipse = TRUE, ellipse.prob = 1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =5,
         varname.adjust = 2,labels =rownames(abio_n),labels.size = 5 )
abio_n_pc=PC_abio_n$x[,c(1,2)]
abio_n_pc

```

##for Mating
```{r}
abio_m=subset(abio,select = c(Clay, Sand, Magnesium, Carbon,pH))
PC_abio_m=prcomp(abio_m,scale. = T)
ggbiplot(pcobj = PC_abio_m,choices =1:2,obs.scale = 0.2, var.scale = 1, 
         ellipse = TRUE, ellipse.prob = 1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =5,
         varname.adjust = 2,labels =rownames(abio_m),labels.size = 5 )
abio_m_pc=PC_abio_m$x[,c(1,2)]
abio_m_pc
```
##for Hatching
```{r}
abio_h=subset(abio,select = c(Clay, Sand, Magnesium, Carbon, Nitrogen, pH))
PC_abio_h=prcomp(abio_h,scale. = T)
ggbiplot(pcobj = PC_abio_h,choices =1:2,obs.scale = 0.2, var.scale = 1, 
         ellipse = TRUE, ellipse.prob = 1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =5,
         varname.adjust = 2,labels =rownames(abio_h),labels.size = 5 )
abio_h_pc=PC_abio_h$x[,c(1,2)]
abio_h_pc
```
##for Fledging
```{r}
abio_f=subset(abio,select = c(Clay, Magnesium, Carbon, Nitrogen, pH))
PC_abio_f=prcomp(abio_f,scale. = T)
ggbiplot(pcobj = PC_abio_f,choices =1:2,obs.scale = 0.2, var.scale = 1, 
         ellipse = TRUE, ellipse.prob = 1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =5,
         varname.adjust = 2,labels =rownames(abio_f),labels.size = 5 )
abio_f_pc=PC_abio_f$x[,c(1,2)]
abio_f_pc
```

#All predictor principal component
##reproductive
```{r}
names(newdfab1)
colnames(newdfab1)=c("pH","Electrical conductivity","Iron","Aluminium","Carbon","Nitrogen","Calcium","Potassium","Sodium","Magnesium","Cation exchange capacity","Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera","Lepidoptera","Breeder : Helper","Reproductive success")

all_r=subset(newdfab1,select = c(Lepidoptera,Ant,Wasp,Bee,Damselfly,Dragonfly,Carbon,Nitrogen, `Breeder : Helper`))
PC_all_r=prcomp(all_r,scale. = T)
ggbiplot(pcobj = PC_all_r,choices =1:2,obs.scale = 0.5, var.scale = 1, 
         ellipse = TRUE, ellipse.prob =1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =3.5,
         varname.adjust = 2,labels =rownames(all_r),labels.size = 5 )
all_r_pc=PC_all_r$x[,c(1,2)]
all_r_pc

```

##nesting
```{r}
colnames(newdfab2)=c("pH","Electrical conductivity","Iron","Aluminium","Carbon","Nitrogen","Calcium","Potassium","Sodium","Magnesium","Cation exchange capacity","Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera","Lepidoptera","Breeder : Helper","Nesting success")

all_n=subset(newdfab2,select = c(Lepidoptera,Damselfly,Dragonfly,Clay, Sand, Magnesium, Carbon, Nitrogen, Iron,pH, `Breeder : Helper`))
PC_all_n=prcomp(all_n,scale. = T)
ggbiplot(pcobj = PC_all_n,choices =1:2,obs.scale = 0.4, var.scale = 1, 
         ellipse = TRUE, ellipse.prob =1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =3.5,
         varname.adjust = 3,labels =rownames(all_n),labels.size = 5 )
all_n_pc=PC_all_n$x[,c(1,2)]
all_n_pc
```
##mating
```{r}
colnames(newdfab3)=c("pH","Electrical conductivity","Iron","Aluminium","Carbon","Nitrogen","Calcium","Potassium","Sodium","Magnesium","Cation exchange capacity","Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera","Lepidoptera","Breeder : Helper","Mating success")

all_m=subset(newdfab2,select = c(Lepidoptera,Damselfly,Dragonfly,
                                 Clay, Sand, Magnesium, Carbon,pH, `Breeder : Helper`))
PC_all_m=prcomp(all_m,scale. = T)
ggbiplot(pcobj = PC_all_m,choices =1:2,obs.scale = 0.4, var.scale = 1, 
         ellipse = TRUE, ellipse.prob =1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =3.5,
         varname.adjust = 3,labels =rownames(all_m),labels.size = 5 )
all_m_pc=PC_all_m$x[,c(1,2)]
all_m_pc

```
##hatching
```{r}
colnames(newdfab4)=c("pH","Electrical conductivity","Iron","Aluminium","Carbon","Nitrogen","Calcium","Potassium","Sodium","Magnesium","Cation exchange capacity","Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera","Lepidoptera","Breeder : Helper","Hatching success")

all_h=subset(newdfab4,select = c(Lepidoptera,Bee,Damselfly,Dragonfly,
                                 Clay, Sand, Magnesium, Carbon, Nitrogen, pH, `Breeder : Helper`))
PC_all_h=prcomp(all_h,scale. = T)
ggbiplot(pcobj = PC_all_h,choices =1:2,obs.scale = 0.4, var.scale = 1, 
         ellipse = TRUE, ellipse.prob =1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =3.5,
         varname.adjust = 3,labels =rownames(all_h),labels.size = 5 )
all_h_pc=PC_all_h$x[,c(1,2)]
all_h_pc

```
##fledging
```{r}
colnames(newdfab5)=c("pH","Electrical conductivity","Iron","Aluminium","Carbon","Nitrogen","Calcium","Potassium","Sodium","Magnesium","Cation exchange capacity","Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera","Lepidoptera","Breeder : Helper","Fledging success")

all_f=subset(newdfab5,select = c(Lepidoptera,Damselfly,Dragonfly,
                                 Clay, Magnesium, Carbon, Nitrogen, pH, `Breeder : Helper`))
PC_all_f=prcomp(all_f,scale. = T)
ggbiplot(pcobj = PC_all_f,choices =1:2,obs.scale = 0.4, var.scale = 1, 
         ellipse = TRUE, ellipse.prob =1,
         circle = TRUE,alpha = 0.5,
         circle.prob = 0.5,varname.size =3.5,
         varname.adjust = 3,labels =rownames(all_f),labels.size = 5 )
all_f_pc=PC_all_f$x[,c(1,2)]
all_f_pc


```
#Linear regression with principal component
##All
###reproductive
```{r}

fit_all_r=lm(newdfab1$`Reproductive success`~all_r_pc[,1])
summary(fit_all_r)
RMSE_all_r=mean(fit_all_r$residuals^2);RMSE_all_r
```
###nesting
```{r}

fit_all_n=lm(newdfab2$`Nesting success`~all_n_pc[,1])
summary(fit_all_n)
RMSE_all_n=mean(fit_all_n$residuals^2);RMSE_all_n
```
###mating
```{r}

fit_all_m=lm(newdfab3$`Mating success`~all_m_pc[,1])
summary(fit_all_m)
RMSE_all_m=mean(fit_all_m$residuals^2);RMSE_all_m
```
###hatching
```{r}

fit_all_h=lm(newdfab4$`Hatching success`~all_h_pc[,1])
summary(fit_all_h)
RMSE_all_h=mean(fit_all_h$residuals^2);RMSE_all_h
```
###fledging
```{r}

fit_all_f=lm(newdfab5$`Fledging success`~all_f_pc[,1])
summary(fit_all_f)
RMSE_all_f=mean(fit_all_f$residuals^2);RMSE_all_f
```
##Abiotic
```{r}

fit_abio_r=lm(newdfab1$`Reproductive success`~abio_r_pc[,1])
summary(fit_abio_r)
RMSE_abio_r=mean(fit_abio_r$residuals^2);RMSE_abio_r
```
###nesting
```{r}

fit_abio_n=lm(newdfab2$`Nesting success`~abio_n_pc[,1])
summary(fit_abio_n)
RMSE_abio_n=mean(fit_abio_n$residuals^2);RMSE_abio_n
```
###mating
```{r}

fit_abio_m=lm(newdfab3$`Mating success`~abio_m_pc[,1])
summary(fit_abio_m)
RMSE_abio_m=mean(fit_abio_m$residuals^2);RMSE_abio_m
```
###hatching
```{r}

fit_abio_h=lm(newdfab4$`Hatching success`~abio_h_pc[,1])
summary(fit_abio_h)
RMSE_abio_h=mean(fit_abio_h$residuals^2);RMSE_abio_h
```
###fledging
```{r}

fit_abio_f=lm(newdfab5$`Fledging success`~abio_f_pc[,1])
summary(fit_abio_f)
RMSE_abio_f=mean(fit_abio_f$residuals^2);RMSE_abio_f
```
##Biotic
###reproductive
```{r}

fit_bio_r=lm(newdfab1$`Reproductive success`~bio_r_pc[,1])
summary(fit_bio_r)
RMSE_bio_r=mean(fit_bio_r$residuals^2);RMSE_bio_r
```
###nesting
```{r}

fit_bio_n=lm(newdfab2$`Nesting success`~bio_n_pc[,1])
summary(fit_bio_n)
RMSE_bio_n=mean(fit_bio_n$residuals^2);RMSE_bio_n
```
###mating
```{r}

fit_bio_m=lm(newdfab3$`Mating success`~bio_m_pc[,1])
summary(fit_bio_m)
RMSE_bio_m=mean(fit_bio_m$residuals^2);RMSE_bio_m
```
###hatching
```{r}

fit_bio_h=lm(newdfab4$`Hatching success`~bio_h_pc[,1])
summary(fit_bio_h)
RMSE_bio_h=mean(fit_bio_h$residuals^2);RMSE_bio_h
```
###fledging
```{r}

fit_bio_f=lm(newdfab5$`Fledging success`~bio_f_pc[,1])
summary(fit_bio_f)
RMSE_bio_f=mean(fit_bio_f$residuals^2);RMSE_bio_f
```
#ANN-L with significant factors only
##All
###Reproductive
```{r}
all_r$r_s=newdfab1$`Reproductive success`
names(all_r)
all_r_new=subset(all_r,select = -c(`Breeder : Helper`))
all_r_new$ratio=all_r$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_r_new)
indexab1 <- sample( seq_len ( nrow ( all_r_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_r_new , 2 , max)#2 indicates column
minab1 = apply(all_r_new, 2 , min)
scaledab1= as.data.frame(scale(all_r_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=9#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Ant+Wasp+Bee+Damselfly+Dragonfly+Carbon+Nitrogen+ratio
                                ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 500)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(9)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_r_new$r_s)
                                                                      - min(all_r_new$r_s))) + min(all_r_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_r_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_r_l
```
###NESTING
```{r}
all_n$r_s=newdfab2$`Nesting success`
names(all_n)
all_n_new=subset(all_n,select = -c(`Breeder : Helper`))
all_n_new$ratio=all_n$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_n_new)
indexab1 <- sample( seq_len ( nrow ( all_n_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_n_new , 2 , max)#2 indicates column
minab1 = apply(all_n_new, 2 , min)
scaledab1= as.data.frame(scale(all_n_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=9#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Damselfly+Dragonfly+Clay+Sand+Magnesium+Carbon+Nitrogen+Iron+pH+ratio
                                ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 500)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(9)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_n_new$r_s)
                                                                      - min(all_n_new$r_s))) + min(all_n_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_n_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_n_l

```
###Mating
```{r}
all_m$r_s=newdfab3$`Mating success`
names(all_m)
all_m_new=subset(all_m,select = -c(`Breeder : Helper`))
all_m_new$ratio=all_m$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_m_new)
indexab1 <- sample( seq_len ( nrow ( all_m_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_m_new , 2 , max)#2 indicates column
minab1 = apply(all_m_new, 2 , min)
scaledab1= as.data.frame(scale(all_m_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=9#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Damselfly+Dragonfly+
                                Clay+Sand+Magnesium+Carbon+pH+ratio
                                ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 500)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(9)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_m_new$r_s)
                                                                      - min(all_m_new$r_s))) + min(all_m_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_m_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_m_l

```

###Hatching
```{r}
all_h$r_s=newdfab4$`Hatching success`
names(all_h)
all_h_new=subset(all_h,select = -c(`Breeder : Helper`))
all_h_new$ratio=all_h$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_h_new)
indexab1 <- sample( seq_len ( nrow ( all_h_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_h_new , 2 , max)#2 indicates column
minab1 = apply(all_h_new, 2 , min)
scaledab1= as.data.frame(scale(all_h_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=ncol(trainNNab1)#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Bee+Damselfly+Dragonfly+Clay+Sand+Magnesium+Carbon+Nitrogen+pH+ratio,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 10)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(12)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_h_new$r_s)
                                                                      - min(all_h_new$r_s))) + min(all_h_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_h_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_h_l

```

###Fledging
```{r}

all_f$r_s=newdfab5$`Fledging success`
names(all_f)
all_f_new=subset(all_f,select = -c(`Breeder : Helper`))
all_f_new$ratio=all_f$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_f_new)
indexab1 <- sample( seq_len ( nrow ( all_f_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_f_new , 2 , max)#2 indicates column
minab1 = apply(all_f_new, 2 , min)
scaledab1= as.data.frame(scale(all_f_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=ncol(trainNNab1)#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Damselfly+Dragonfly+
                                        Clay+Magnesium+Carbon+Nitrogen+pH+ratio
                                ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 10)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(9)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_f_new$r_s)
                                                                      - min(all_f_new$r_s))) + min(all_f_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_f_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_f_l

```
#ANN-NL with significan factors
##All
###Repro
```{r}
all_r$r_s=newdfab1$`Reproductive success`
names(all_r)
all_r_new=subset(all_r,select = -c(`Breeder : Helper`))
all_r_new$ratio=all_r$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_r_new)
indexab1 <- sample( seq_len ( nrow ( all_r_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_r_new , 2 , max)#2 indicates column
minab1 = apply(all_r_new, 2 , min)
scaledab1= as.data.frame(scale(all_r_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=9#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Ant+Wasp+Bee+Damselfly+Dragonfly+Carbon+Nitrogen+ratio
                                ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 500)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(9)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_r_new$r_s)
                                                                      - min(all_r_new$r_s))) + min(all_r_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_r_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_r_nl


```
###Nesting
```{r}
all_n$r_s=newdfab2$`Nesting success`
names(all_n)
all_n_new=subset(all_n,select = -c(`Breeder : Helper`))
all_n_new$ratio=all_n$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_n_new)
indexab1 <- sample( seq_len ( nrow ( all_n_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_n_new , 2 , max)#2 indicates column
minab1 = apply(all_n_new, 2 , min)
scaledab1= as.data.frame(scale(all_n_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=9#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Damselfly+Dragonfly+Clay+Sand+Magnesium+Carbon+Nitrogen+Iron+pH+ratio
                                ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = F,rep = 500)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(9)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_n_new$r_s)
                                                                      - min(all_n_new$r_s))) + min(all_n_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_n_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_n_nl


```
###Mating
```{r}
all_m$r_s=newdfab3$`Mating success`
names(all_m)
all_m_new=subset(all_m,select = -c(`Breeder : Helper`))
all_m_new$ratio=all_m$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_m_new)
indexab1 <- sample( seq_len ( nrow ( all_m_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_m_new , 2 , max)#2 indicates column
minab1 = apply(all_m_new, 2 , min)
scaledab1= as.data.frame(scale(all_m_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=9#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Damselfly+Dragonfly+
                                        Clay+Sand+Magnesium+Carbon+pH+ratio
                                ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = F,rep = 50)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(9)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_m_new$r_s)
                                                                      - min(all_m_new$r_s))) + min(all_m_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_m_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_m_nl

```

###hatching
```{r}
all_h$r_s=newdfab4$`Hatching success`
names(all_h)
all_h_new=subset(all_h,select = -c(`Breeder : Helper`))
all_h_new$ratio=all_h$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_h_new)
indexab1 <- sample( seq_len ( nrow ( all_h_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_h_new , 2 , max)#2 indicates column
minab1 = apply(all_h_new, 2 , min)
scaledab1= as.data.frame(scale(all_h_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=ncol(trainNNab1)#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Bee+Damselfly+Dragonfly+
                                        Clay+Sand+Magnesium+Carbon+Nitrogen+pH+ratio
                                ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = F,rep = 50)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(11)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_h_new$r_s)
                                                                      - min(all_h_new$r_s))) + min(all_h_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_h_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_h_nl

```

###fledging
```{r}

all_f$r_s=newdfab5$`Fledging success`
names(all_f)
all_f_new=subset(all_f,select = -c(`Breeder : Helper`))
all_f_new$ratio=all_f$`Breeder : Helper`
######r_s
set.seed(5)
samplesize = 0.70 * nrow(all_f_new)
indexab1 <- sample( seq_len ( nrow ( all_f_new ) ), size = samplesize )
indexab1

maxab1 = apply(all_f_new , 2 , max)#2 indicates column
minab1 = apply(all_f_new, 2 , min)
scaledab1= as.data.frame(scale(all_f_new, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=ncol(trainNNab1)#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
        for (j in l2) {
                NNab1=neuralnet(formula =r_s~Lepidoptera+Damselfly+Dragonfly+
                                        Clay+Magnesium+Carbon+Nitrogen+pH+ratio
                                ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = F,rep = 500)
                predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(9)])
                predict_reultNNab1 = (predict_testNNab1$net.result * (max(all_f_new$r_s)
                                                                      - min(all_f_new$r_s))) + min(all_f_new$r_s)
                predict_reultNNab1
                #plot(testN1$r_s, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
                
                oriab1=testNab1$r_s
                RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
                RMSE.NNab1[i,j]
        }
        
}
#names(testNab1)
dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_all_f_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_all_f_nl
```
#ANN-L with all factors
##Reproductive
```{r}
names(newdfab1)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")

names(newdfab1)
######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab1)
indexab1 <- sample( seq_len ( nrow ( newdfab1 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab1 , 2 , max)#2 indicates column
minab1 = apply(newdfab1, 2 , min)
scaledab1= as.data.frame(scale(newdfab1, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab1$R_S)
                                                          - min(newdfab1$R_S))) + min(newdfab1$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_r_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_r_l



```
##Nesting
```{r}
names(newdfab2)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")


######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab2)
indexab1 <- sample( seq_len ( nrow ( newdfab2 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab2 , 2 , max)#2 indicates column
minab1 = apply(newdfab2, 2 , min)
scaledab1= as.data.frame(scale(newdfab2, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab2$R_S)
                                                          - min(newdfab2$R_S))) + min(newdfab2$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_n_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_n_l

```
##Mating
```{r}
names(newdfab3)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")


######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab3)
indexab1 <- sample( seq_len ( nrow ( newdfab3 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab3 , 2 , max)#2 indicates column
minab1 = apply(newdfab3, 2 , min)
scaledab1= as.data.frame(scale(newdfab3, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab3$R_S)
                                                          - min(newdfab3$R_S))) + min(newdfab3$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_m_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_m_l

```
##Hatching
```{r}
names(newdfab4)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")


######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab4)
indexab1 <- sample( seq_len ( nrow ( newdfab4 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab4 , 2 , max)#2 indicates column
minab1 = apply(newdfab4, 2 , min)
scaledab1= as.data.frame(scale(newdfab4, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab4$R_S)
                                                          - min(newdfab4$R_S))) + min(newdfab4$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_h_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_h_l


```
##Fledging
```{r}
names(newdfab5)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")


######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab5)
indexab1 <- sample( seq_len ( nrow ( newdfab5 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab5 , 2 , max)#2 indicates column
minab1 = apply(newdfab5, 2 , min)
scaledab1= as.data.frame(scale(newdfab5, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = T,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab5$R_S)
                                                          - min(newdfab5$R_S))) + min(newdfab5$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_f_l=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_f_l


```
#ANN-NL with all factors
##Reproductive
```{r}
names(newdfab1)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")

names(newdfab1)
######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab1)
indexab1 <- sample( seq_len ( nrow ( newdfab1 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab1 , 2 , max)#2 indicates column
minab1 = apply(newdfab1, 2 , min)
scaledab1= as.data.frame(scale(newdfab1, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = F,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab1$R_S)
                                                          - min(newdfab1$R_S))) + min(newdfab1$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_r_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_r_nl



```
##Nesting
```{r}
names(newdfab2)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")


######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab2)
indexab1 <- sample( seq_len ( nrow ( newdfab2 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab2 , 2 , max)#2 indicates column
minab1 = apply(newdfab2, 2 , min)
scaledab1= as.data.frame(scale(newdfab2, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = F,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab2$R_S)
                                                          - min(newdfab2$R_S))) + min(newdfab2$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_n_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_n_nl

```
##Mating
```{r}
names(newdfab3)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")


######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab3)
indexab1 <- sample( seq_len ( nrow ( newdfab3 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab3 , 2 , max)#2 indicates column
minab1 = apply(newdfab3, 2 , min)
scaledab1= as.data.frame(scale(newdfab3, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = F,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab3$R_S)
                                                          - min(newdfab3$R_S))) + min(newdfab3$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_m_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_m_nl

```
##Hatching
```{r}
names(newdfab4)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")


######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab4)
indexab1 <- sample( seq_len ( nrow ( newdfab4 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab4 , 2 , max)#2 indicates column
minab1 = apply(newdfab4, 2 , min)
scaledab1= as.data.frame(scale(newdfab4, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = F,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab4$R_S)
                                                          - min(newdfab4$R_S))) + min(newdfab4$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_h_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_h_nl


```
##Fledging
```{r}
names(newdfab5)=c("pH","EC","Fe","Al" ,"C" ,"N","Ca","K","Na","Mg","CEC",
                  "Sand","Silt","Clay","Dragonfly","Damselfly","Homoptera","Bee","Wasp","Ant","Orthoptera",
                  "Lepidoptera","socio","R_S")


######R_S
set.seed(5)
samplesize = 0.70 * nrow(newdfab5)
indexab1 <- sample( seq_len ( nrow ( newdfab5 ) ), size = samplesize )
indexab1

maxab1 = apply(newdfab5 , 2 , max)#2 indicates column
minab1 = apply(newdfab5, 2 , min)
scaledab1= as.data.frame(scale(newdfab5, center = minab1, scale = maxab1 - minab1))

trainNNab1= scaledab1[indexab1 , ]
testNab1 = scaledab1[-indexab1 , ]

dim(trainNNab1)
names(trainNNab1)
#number of hidden nodes for 2 layered
m1=1;n1=23#m1=output #n1 = input # Huang (2003)
a1=round(sqrt((m1+2)*n1)+2*sqrt(n1/(m1+2)))#number of hidden nodes for first layer
a1
b1=round(m1*sqrt(n1/(m1+2)))#number of hidden nodes for second layer
b1
l1=seq(1,a1)#number of nodes
l2=seq(1,b1)#number of layers
RMSE.NNab1=matrix(data=NA,nrow = a1,ncol = b1)
l1;l2
names(trainNNab1)
#plot(NNab1)
for (i in l1) {
  for (j in l2) {
    NNab1=neuralnet(formula =R_S~pH+EC+Fe+Al+C+N+Ca+K+Na+Mg+CEC+Sand+Silt+Clay+
                      Dragonfly+Damselfly+Homoptera+Bee+Wasp+Ant+Orthoptera+Lepidoptera+socio
                    ,data = trainNNab1, hidden = c(l1[i],l2[j]), linear.output = F,rep = 500)
    predict_testNNab1 = neuralnet::compute(NNab1, testNab1[,-c(24)])
    predict_reultNNab1 = (predict_testNNab1$net.result * (max(newdfab5$R_S)
                                                          - min(newdfab5$R_S))) + min(newdfab5$R_S)
    predict_reultNNab1
    #plot(testN1$R_S, predict_reultNN, col='blue', pch=16, ylab = "Predicted Conditional fledging success NN", xlab = "Observed Conditional fledging success NN")
    
    oriab1=testNab1$R_S
    RMSE.NNab1[i,j] = (sum((oriab1 - predict_reultNNab1)^2) / nrow(testNab1)) ^ 0.5
    RMSE.NNab1[i,j]
  }
  
}

dim(RMSE.NNab1)
NNab1_RMSE_layer=plot_ly(x=~l2,y=~l1,z=~RMSE.NNab1,type = 'contour')
NNab1_RMSE_layer;RMSE.NNab2_socio_f_nl=min(RMSE.NNab1)
#Select the nodes per layer with least RMSE by moving the cursor in viewer of R
RMSE.NNab2_socio_f_nl


```

#Comarison of models
##Linear models
```{r}
Modelnames=c("Reproductive success (PC: all correlated)",
             "Nesting success (PC: all correlated)",
             "Mating success (PC: all correlated)",
             "Hatching success (PC: all correlated)",
             "Fledging success (PC: all correlated)",
             "Reproductive success (PC: all correlated abiotic)",
             "Nesting success (PC: all correlated abiotic)",
             "Mating success (PC: all correlated abiotic)",
             "Hatching success (PC: all correlated abiotic)",
             "Fledging success (PC: all correlated abiotic)",
             "Reproductive success (PC: all correlated biotic)",
             "Nesting success (PC: all correlated biotic)",
             "Mating success (PC: all correlated biotic)",
             "Hatching success (PC: all correlated biotic)",
             "Fledging success (PC: all correlated biotic)")
cl1=c("#990F0F","#99540F","#6B990F","#0F6B99","#260F99",
      "#990F0F","#99540F","#6B990F","#0F6B99","#260F99",
      "#990F0F","#99540F","#6B990F","#0F6B99","#260F99")
RMSELM=c(RMSE_all_r,RMSE_all_n,RMSE_all_m,RMSE_all_h,RMSE_all_f,
         RMSE_abio_r,RMSE_abio_n,RMSE_abio_m,RMSE_abio_h,RMSE_abio_f,
         RMSE_bio_r,RMSE_bio_n,RMSE_bio_m,RMSE_bio_h,RMSE_bio_f)
length(RMSELM)
par( mar=c (20,2,1,1))
barplot(RMSELM,col=cl1, names.arg=Modelnames,las=3,ylim=c(0,0.05), main="RMSE values of linear regressions with principal components")
```
##ANN
```{r}
ANNnames=c("Reproductive success (All prdeictors ANN-L)",
             "Nesting success (All prdeictors ANN-L)",
             "Mating success (All prdeictors ANN-L)",
             "Hatching success (All prdeictors ANN-L)",
             "Fledging success (All prdeictors ANN-L)",
             "Reproductive success (All prdeictors ANN-NL)",
             "Nesting success (All prdeictors ANN-NL)",
             "Mating success (All prdeictors ANN-NL)",
             "Hatching success (All prdeictors ANN-NL)",
             "Fledging success (All prdeictors ANN-NL)",
             "Reproductive success (All correlated prdeictors ANN-L)",
             "Nesting success (All correlated prdeictors ANN-L)",
             "Mating success (All correlated prdeictors ANN-L)",
             "Hatching success (All correlated prdeictors ANN-L)",
             "Fledging success (All correlated prdeictors ANN-L)",
             "Reproductive success (All correlated prdeictors ANN-NL)",
             "Nesting success (All correlated prdeictors ANN-NL)",
             "Mating success (All correlated prdeictors ANN-NL)",
             "Hatching success (All correlated prdeictors ANN-NL)",
             "Fledging success (All correlated prdeictors ANN-NL)")
RMSEANN=c(RMSE.NNab2_socio_r_l,
          RMSE.NNab2_socio_n_l,
          RMSE.NNab2_socio_m_l,
          RMSE.NNab2_socio_h_l,
          RMSE.NNab2_socio_f_l,
          RMSE.NNab2_socio_r_nl,
          RMSE.NNab2_socio_n_nl,
          RMSE.NNab2_socio_m_nl,
          RMSE.NNab2_socio_h_nl,
          RMSE.NNab2_socio_f_nl,
          RMSE.NNab2_all_r_l,
          RMSE.NNab2_all_n_l,
          RMSE.NNab2_all_m_l,
          RMSE.NNab2_all_h_l,
          RMSE.NNab2_all_f_l,
          RMSE.NNab2_all_r_nl,
          RMSE.NNab2_all_n_nl,
          RMSE.NNab2_all_m_nl,
          RMSE.NNab2_all_h_nl,
          RMSE.NNab2_all_f_nl)
cl2=c("#990F0F","#99540F","#6B990F","#0F6B99","#260F99",
      "#990F0F","#99540F","#6B990F","#0F6B99","#260F99",
      "#990F0F","#99540F","#6B990F","#0F6B99","#260F99",
      "#990F0F","#99540F","#6B990F","#0F6B99","#260F99")
par( mar=c (20,2,1,1))
barplot(RMSEANN,col=cl2, names.arg=ANNnames,las=3,ylim=c(0,.6), main="RMSE values of ANNs with maximum number of predictors")

```


